Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
new section

\section{Design}
After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc. But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention. To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool. \\

\noindent {\bfseries Overview}
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

>>>>

\section{Wut new section} 
perhaps a section on the state of censorship technologies today, and how to evaluate censorship circumvention tools sketching here. This gives our work scope and some purpose. Our work examines one of many facets which make a censorship circumvention tool a good one, and it's the usability of the system.

%moved this up to this new section 
After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc. But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention. To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.

\section{Design}
\noindent {\bfseries Overview}
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
